Stage-Splitting a Modal Language

### 2014-08-29 paper/splitting.tex
worked on intro to splitting

The stage splitting operation takes as input a \lang\ term which contains interleaved stage \bbone\ and stage \bbtwo\ code
and splits it into two separate terms: one with all of the stage \bbone\ code and one with all the stage \bbtwo\ code.  
To facilitate communication between the stages, there is a data structure passed between the stages, 
which is an output of the stage \bbone\ term and and input to the stage \bbtwo\ term.

As with the dynamics, the form of the splitting statement depends on the external stage of the term.
We consider splitting of stage \bbtwo\ terms first, as it has a simpler form.  
For example, consider \verb|hold{1+2} < 5|.
We can split this into two separate terms, \verb|1+2| and \verb|fn l => l < 5|, 
which are called the {\em precomputation} and {\em residual}\footnote{We also used the term {\em residual} for the result of partial evaluation.
Where necessary, we will distinguish between these concepts by using the terms {\em splitting-residual}
and {\em evaluation-residual}.}, respectively.

@@

\subsection{Value Splitting}

>>>>

Much like partial evaluation, the goal of stage-splitting is to separate the evaluation of a multi-stage function into distinct phases.
Despite this similarity in purpose, the form of stage-splitting is rather different. 
Taking a multivariate function $f$ as input, stage-splitting produces two functions $f_1$ and $f_2$,
where $f_1$ uses the stage-\bbone\ input to produce a data structure, 
and $f_2$ uses that data structure and the stage-\bbtwo\ input to produce the final output.  
More precisely, a stage splitter is any $s$ such that
\[
	\forall f. \exists f_1,f_2. 
	\left[
		\begin{array}{l}
		s(f) = (f_1,f_2) \text{ and } \\
		\forall x,y.\llbracket f \rrbracket(x,y)=\llbracket f_2 \rrbracket(\llbracket f_1 \rrbracket(x),y)
		\end{array}
	\right]
\]
with the same $\llbracket \cdot \rrbracket$ notation as before.
Importantly, the stage splitting operation does not depend on the stage-\bbone\ input, unlike partial evaluation.

As with the dynamics, our stage-splitting algorithm for expressions in \lang\ take 
the form of two mutually-dependent judgments, $\splitonesym$ and $\splittwosym$. 
Before diving into the full generality, we consider splitting for a simple fragment of the full language: partial values.

\subsection{Partial Value Splitting}

\subsection{Full Expression Splitting}

We consider splitting of stage \bbtwo\ terms first, as it has a simpler form.  
For example, consider \verb|hold{1+2} < 5|.
We can split this into two separate terms, \verb|1+2| and \verb|fn l => l < 5|, 
which are called the {\em precomputation} and {\em residual}\footnote{We also used the term {\em residual} for the result of partial evaluation.
Where necessary, we will distinguish between these concepts by using the terms {\em splitting-residual}
and {\em evaluation-residual}.}, respectively.

@@
